\documentclass[margin, line, 10pt]{res}
\oddsidemargin -.5in
\evensidemargin -.5in
\textwidth=6.0in
\itemsep=0in
\parsep=0in
\usepackage{scrextend}
\usepackage{hyperref}
\usepackage{color}
\usepackage{changepage}% http://ctan.org/pkg/changepage
\usepackage{lipsum}%

\hypersetup{
    colorlinks=true,       % false: boxed links; true: colored links
    linkcolor=cyan,          % color of internal links (change box color with linkbordercolor)
    citecolor=green,        % color of links to bibliography
    filecolor=magenta,      % color of file links
    urlcolor=cyan           % color of external links
}

\newenvironment{list1}{
  \begin{list}{\ding{113}}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in}
      \setlength{\leftmargin}{0.17in}}}{\end{list}}
\newenvironment{list2}{
  \begin{list}{$\bullet$}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in}
      \setlength{\leftmargin}{0.2in}}}{\end{list}}
\begin{document}
 \textbf{\LARGE Prashanth Iyer}
\vspace{.15cm} \\
\vspace{-.05cm}
\begin{resume}

\section{Contact Information}
\vspace{.05in}
\begin{tabular}{@{}p{3in}p{3in}}
{\it E-mail:} \href{mailto:munichlinux@gmail.com}{munichlinux@gmail.com} & {\it Git:} \href{http://github.com/munichlinux}{http://github.com/munichlinux} \\
{\it Current Location:} Sunnyvale, US. \\
{\it Mobile:}  +1(415) 622-5201.
\end{tabular}

\section{Bio}
\{
  \begin{addmargin}[1em]{0em}
  {\bf rant}: [NodeJS, ES2015, ES2016, Functional Programming, Generator awesomeness],\\
  {\bf me}: [passionate programmer, love design patterns, frequent hiker, budding photographer],
  \end{addmargin}
  \vspace{-.15in}
\}

\section{Education}
{\bf B.Tech Information Technology}, Anna University, India. \hfill (June 2003 - Nov 2007)

\section{Skills}
\begin{list2}
\item {\bf Languages:} NodeJS, Python.\\
\vspace{-.3cm}
\item {\bf DevOps:} Docker, Ansible, Kubernetes, gulp, browserify.\\
\vspace{-.3cm}
\item {\bf JavaScript Lib:} JQuery, Backbone.js, Lodash.\\
\vspace{-.3cm}
\item {\bf Web:} HTML5, CSS3, WebSockets, Web Components, Polymer, React.\\
\vspace{-.3cm}
\item {\bf CSS Preprocessors:} Sass, Compass.\\
\vspace{-.3cm}
\item {\bf Web Frameworks:} Django, Express.\\
\vspace{-.3cm}
\item {\bf Operating System:} GNU/Linux, Macintosh.\\
\vspace{-.3cm}
\item {\bf Version Control:} Subversion, Git.\\
\vspace{-.3cm}
\item {\bf API:} OAuth, OpenId.\\
\vspace{-.3cm}
\item {\bf Database:} MySQL, CouchDB, PostgreSQL.\\
\vspace{-.3cm}
\item {\bf Certification:} RHCT(604006875597323).\\
\vspace{-.3cm}
\item {\bf Favorite Text Editors:} GNUEmacs, Sublime Text, Atom.\\
\vspace{-.3cm}
\end{list2}

\section{Employment}

{\Large {\bf Search, Yahoo Inc.}}, Software Dev Eng, Sr. (December 2015 - current)\\
\begin{adjustwidth}{.5em}{0pt}
  \vspace{-.1cm}
  I am part of the search Mobile SDK team; I build the backend API for the syndication network.
  \begin{list2}
  \vspace{.2cm}
  \item Scaled the API to 4000 QPS.
  \item Build fraud detection for the syndication network.
  \end{list2}
  \vspace{.05cm}

\end{adjustwidth}
\vspace{.05cm}

{\Large {\bf Mobius Justice}}, co-founder (June 2016 - April 2017)\\
\begin{adjustwidth}{.5em}{0pt}
  \vspace{-.1cm}
  Mobius is a Outcomes Driven Platform that provides the department of probation with
  insights into the performance of their client population (google analytics for juvenile probation system).

  \begin{list2}
  \vspace{.2cm}
  \item The platform was built on Gitlab, GCP, Kubernetes, Docker, NodeJS, PostgreSQL, React.
  \item Unit testing framework for database queries; a system that can generate sample data set, create sandbox environment, and test SQL.
  \item Library to write queries with \href{https://en.wikipedia.org/wiki/Function_composition_(computer_science)}{Function composition}.
  \end{list2}
  \vspace{.05cm}

\end{adjustwidth}
\vspace{.05cm}

{\Large {\bf YSB, Yahoo Inc.}}, Software Dev Eng, Sr. (November 2013 - November 2015)\\
\vspace{-.1cm}
\begin{list2}
\vspace{.1cm}
\item Rewrote the legacy stack with NodeJS, made the application device friendly.
\item Built A/B testing infrastructure, analytics platform, and continuous deployment.
\item Reduced development cycle from weeks to hours.
\item Ported clumsy deployment into single click deployment model.
\item Rebuilt the payments system with Zuora.
\item Migrated from Y\textsc{\char13}s infrastructure to AWS.
\end{list2}
\vspace{.05cm}

{\Large {\bf Flickr, Yahoo Inc.}}, Lead Engineer, San Francisco, CA.  \hfill (April 2013 - Oct 2013)\\
\vspace{-.1cm}

{\Large {\bf Webhosting, Yahoo Inc.}}, Lead Engineer, Bangalore, India  \hfill (July 2010 - March 2013)\\
\vspace{-.1cm}
\begin{adjustwidth}{.5em}{0pt}
I started as Sr.Software Engineer, in a year time moved to a lead role.\\
\vspace{-.1cm}
\begin{list2}
\vspace{-.3cm}
\item Re-architected the old PHP stack to NodeJS.\\
\vspace{-.3cm}
\item Redesigned the major parts of the framework to prototype and deliver faster.\\
\vspace{-.3cm}
\item Build Template testing framework which reduced the testing cost by one-third.\\
\vspace{-.3cm}
\item Introduced Frontend best practices, TDD and BDD.\\
\end{list2}
\vspace{.05cm}
\end{adjustwidth}

\section{}
{\Large {\bf Sportxiom Ventures}}, Web Architect, Hyderabad, India  \hfill 2009 - 2010\\
\vspace{-.3cm}\\
Took a position as Web Architect in a bootstrapping startup, I was responsible for building a real time sports application in Python, Django, and JavaScript.
\vspace{.05cm}

\section{}
{\Large {\bf Info Edge}}, Senior Software Engineer,  Noida, India \hfill 2008 - 2009 \\
\vspace{-.3cm}\\
I was part of the brijj.com, I learned JavaScript and fell in love with it. I made lot of UI and Front-end performance improvements.
\vspace{.05cm}


\section{}
{\Large {\bf Cleartrip}}, Graduate Engineer,  Mumbai, India \hfill 2007 - 2008\\
\vspace{-.3cm}\\
I was fresh grad out of college, I was a part of air search team. I learned Lisp, web development, air system.
\vspace{.05cm}

\section{Awards}
\begin{list2}
\item 'The Quality Champ' for the Q2 - 2011 at Yahoo Inc.
\item 'Best Project Award' for 2007, Kongu Engineering College, India.
\end{list2}

\end{resume}
\end{document}
